Building a continuous benchmarking ecosystem in bioinformatics

### 2025-07-23 2_second_review/manuscript.tex
bring back Spack

Finally, scientific software management handling is known for its nuances, including abundant dependencies with known incompatibilities and complex installation recipes \cite{droge2023-ax}. Scientific software management is handled via traditional (Linux) package managers (RPMs, DEBs), central software stacks and environment modules (i.e., Lmod), \texttt{conda}, containers (e.g., \texttt{apptainer} or \texttt{Singularity}; \cite{Kurtzer2017-mn}), or read-only network filesystems providing ready-to-use installations (CernVM-FS) \cite{Blomer2013-jk}. Further strategies are under active development: EESSI \cite{droge2023-ax} and the Digital Research Alliance of Canada \cite{Boissonneault2019-wm} are effectively providing multi-purpose, reusable and efficient software installations via CernVM-FS; \texttt{conda} is speeding up their deployment procedures (via \texttt{py-rattler}/\texttt{pixi}) and allowing compilation to Web assembly (to execute code within a web browser); and \texttt{apptainer} (former \texttt{Singularity}) provides rootless containerization suitable for running in scientific clusters.

>>>>

Finally, scientific software management handling is known for its nuances, including abundant dependencies with known incompatibilities and complex installation recipes \cite{droge2023-ax}. Scientific software management is handled via traditional (Linux) package managers (RPMs, DEBs), automated and reproducible installs (such as \ttexttt{EasyBuild} \cite{Hoste2012-gg} or \texttt{Spack} \cite{Gamblin2015-ll}), central software stacks and environment modules (i.e., Lmod), \texttt{conda}, containers (e.g., \texttt{apptainer} or \texttt{Singularity}; \cite{Kurtzer2017-mn}), or read-only network filesystems providing ready-to-use installations (CernVM-FS) \cite{Blomer2013-jk}. Further strategies are under active development: EESSI \cite{droge2023-ax} and the Digital Research Alliance of Canada \cite{Boissonneault2019-wm} are effectively providing multi-purpose, reusable and efficient software installations via CernVM-FS; \texttt{conda} is speeding up their deployment procedures (via \texttt{py-rattler}/\texttt{pixi}) and allowing compilation to Web assembly (to execute code within a web browser); and \texttt{apptainer} (former \texttt{Singularity}) provides rootless containerization suitable for running in scientific clusters.
